Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package \vskip15pt Supplementary Materials

### 2018-02-27 docs/MEE_submission/manuscript_MEE.tex
small MS change

\section{Directory Structure and Reproducibility}
The \pkg{metaDigitise} package was created with the idea that users would have multiple images to extract from and therefore operates in the same way whether the user has one or multiple images. There is one main function, \fct{metaDigitise}, which interactively takes the user through the process of extracting data from figures. \fct{metaDigitise} works on a directory containing images of figures copied from primary literature, in .png, .jpg, .tiff, .pdf format, specified to \fct{metaDigitise} through the \code{dir} argument. The user needs to think carefully about their directory structure early on in their project, especially if they plan to share the extractions with collaborators or publish the project. Although different directory structures may be used, we would recommend having all files for one project in a single directory with an informative and unambiguous naming scheme for images to help identify the paper and figure that data come from, for example:

\begin{CodeChunk}
\begin{CodeOutput}
* Main project directory
    + FiguresToExtract
        + Paper1_Figure1_trait1.png
        + Paper1_Figure2_trait2.png
        + Paper2_Figure1_trait3.png
\end{CodeOutput}
\end{CodeChunk}

>>>>

\section{Directory Structure and Reproducibility}
The \pkg{metaDigitise} package was created with the idea that users would have multiple images to extract from and therefore operates in the same way whether the user has one or multiple images. There is one main function, \fct{metaDigitise}, which interactively takes the user through the process of extracting data from figures. \fct{metaDigitise} works on a directory containing images of figures copied from primary literature, in .png, .jpg, .tiff, .pdf format, specified to \fct{metaDigitise} through the \code{dir} argument. The user needs to think carefully about their directory structure early on in their project, especially if they plan to share the extractions with collaborators or publish the project. Although different directory structures may be used, we would recommend having all files for one project in a single directory with an informative and unambiguous naming scheme for images to help identify the paper and figure that data come from (e.g. paper_figure_trait.png).
